

```{r setup, include=FALSE}


library(tidyverse)
library(magrittr)
library(ggrepel)
library(vroom)
library(ggdendro)
library(patchwork)

filter <- dplyr::filter


knitr::opts_chunk$set(echo = TRUE)
```


```{r}
read_tsv("./Permutation/annotated_perm_intestine44_age.tsv") -> data_filtered


data_filtered%>%distinct(chr_base)
```







```{r}
data_filtered %>%
select(1:45) %>%
    column_to_rownames('chr_base') %>%
  na.omit() %>%
  t() %>% 
# To calculate the PCA, we will center the data, but not scale it, because 
# methylation data is already scaled from 0% to 100%.
  prcomp(center = T, scale = F) -> pca_data_filt

######

### format results for plotting
# Get the percent variance explained by each PC and save it to a table for
# plotting
tibble(var_explained = ((pca_data_filt$sdev) ^ 2 / (sum(pca_data_filt$sdev ^ 2)))) %>%
  mutate(PC = colnames(pca_data_filt$x), 
         PC = factor(PC, PC)) -> pca_data_scree_filt

# The coordinates to plot the PCA are in the x table of the PCA object.
pca_data_filt$x %>%
  as.data.frame() %>%
  rownames_to_column('filename') %>%
  # Add variables back in to color by.
   mutate(Age = case_when(str_detect(filename, 'Y') ~ '4mo',
                           str_detect(filename, 'M') ~ '12mo', 
                           str_detect(filename, 'N') ~ '18mo', 
                           str_detect(filename, 'O') ~ '24mo'),
          Organ = case_when(str_detect(filename, 'YU|MU|NU|OU') ~ 'USI',
                           str_detect(filename, 'YL|ML|NL|OL') ~ 'LSI', 
                           str_detect(filename, 'YC|MC|NC|OC') ~ 'COL'),
          gfp = case_when(str_detect(filename, '_pos') ~ 'pos',
                           str_detect(filename, '_neg') ~ 'neg'),
         batch = case_when(str_detect(filename, '_24B') ~ '24B',
                           str_detect(filename, '_34B') ~ '34B', 
                           str_detect(filename, '39a') ~ '39a',
                          str_detect(filename, '39b') ~ '39b',
                           str_detect(filename, '60a') ~ '60a',
                           str_detect(filename, '60b') ~ '60b',
                          str_detect(filename, 'nova.cov.gz') ~ 'nova'),
         sample = case_when(str_detect(filename, 'YU') ~ 'YU',
                           str_detect(filename, 'YL') ~ 'YL', 
                           str_detect(filename, 'YC') ~ 'YC',
                           str_detect(filename, 'MU') ~ 'MU',
                           str_detect(filename, 'ML') ~ 'ML', 
                           str_detect(filename, 'MC') ~ 'MC',
                           str_detect(filename, 'NU') ~ 'NU',
                           str_detect(filename, 'NL') ~ 'NL', 
                           str_detect(filename, 'NC') ~ 'NC',
                           str_detect(filename, 'OU') ~ 'OU', 
                           str_detect(filename, 'OL') ~ 'OL', 
                           str_detect(filename, 'OC') ~ 'OC'),
         label = str_remove_all(filename, '.cov.gz'),
           label = str_remove_all(filename, '_24B'),
          label = str_remove_all(filename,  '_34B'),
          label = str_remove_all(filename,  '_39a'),
          label = str_remove_all(filename,  '_39b'),
              label = str_remove_all(filename,  '_60a'),
          label = str_remove_all(filename,  '_60b'),
            label = str_remove_all(filename,  '_gfp'),
                     label = str_remove_all(filename,  './'),
         label = str_remove_all(filename, '.cov')) -> pca_data_filt

######
```






<!-- ```{r,fig.width=5.5, fig.height=4} -->

<!-- # PCA colored by age -->
<!-- pca_data_filt %>%  -->
<!--   tidyr::unite(group,c(sample,batch),sep="_", remove=FALSE) %>% -->
<!--   mutate(Age=factor(Age,levels=c("4mo","12mo","18mo","24mo")))%>% -->
<!-- ggplot(aes(x=PC1, y=PC2)) + -->
<!--   geom_point(aes(fill=Age, shape=Organ), size=5) + -->
<!--    scale_fill_manual(name = 'Age', labels= c("4mo","12mo","18mo","24mo"),values = c("4mo"="forestgreen","12mo"="purple", "18mo"="tomato2","24mo"="gold3")) + -->
<!--  scale_shape_manual(name = 'Organ', values = c("COL"=21,"LSI"=23, "USI"=22)) + -->
<!--   xlab("PC1(25.6%)")+ -->
<!--   ylab("PC2(11.4%)")+  -->
<!--    geom_line(aes(x=PC1, y=PC2, group=group), linetype =3, size=1)+ -->
<!--   # ggrepel::geom_text_repel(aes(label=filename))+ -->
<!--   theme_classic()+ -->
<!--   theme(axis.title.x = element_text(size = 14), axis.title.y = element_text(size = 14), -->
<!--         axis.text.y= element_text(size = 12, face='bold'),axis.text.x= element_text(size = 12, face='bold'),title =element_text(size = 15, face='bold'))+ -->
<!--     theme(plot.title = element_text(size = 15, face = "bold"), -->
<!--              legend.text = element_text(size = 10, face = "bold")) -->

<!-- ``` -->





```{r, fig.width=6,fig.height=4.5}

# PCA colored by age
pca_data_filt %>% 
  tidyr::unite(group,c(sample,batch),sep="_", remove=FALSE) %>%
  mutate(Age=factor(Age,levels=c("4mo","12mo","18mo","24mo")))%>%
ggplot(aes(x=PC1, y=PC2)) +
  geom_point(aes(fill=Age, shape=Organ), size=7) +
   scale_fill_manual(name = 'Age', labels= c("4mo","12mo","18mo","24mo"),values = c("forestgreen","purple", "tomato2","gold3")) +
 scale_shape_manual(name = 'Organ', values = c("COL"=21,"LSI"=23, "USI"=22)) +
  xlab("PC1 (25.6%)")+
  ylab("PC2 (11.4%)")+ 
  coord_cartesian(xlim=c(-2500,2500))+
   geom_line(aes(x=PC1, y=PC2, group=group), linetype =3, size=1)+
  # ggrepel::geom_text_repel(aes(label=filename))+
  theme_classic()+
  theme(legend.position = c(0.93, 0.6))+
  theme(axis.title.x = element_text(size = 20), axis.title.y = element_text(size = 20),
        axis.text.y= element_text(size = 20, face='bold'),axis.text.x= element_text(size = 20, face='bold'),title =element_text(size = 20, face='bold'))+
  theme(plot.title = element_text(size = 20, face = "bold"),
          legend.title = element_text(size = 20, face = "bold"),
             legend.text = element_text(size = 20, face = "bold"))+
  guides(fill = guide_legend(override.aes = list(color = c("forestgreen","purple", "tomato2","gold3"))))->pB


```







```{r}


read_tsv("COL_young_diff_cov20.tsv") %>% mutate(sig=neg_log_qvalue > 1.30102 & abs(meth.diff) > 5)->COL_stem

read_tsv("COL_old_diff_cov20.tsv") %>% mutate(sig=neg_log_qvalue > 1.30102 & abs(meth.diff) > 5)->COL_nonstem


read_tsv("annotated_COL_age_pos_cov20.txt") %>% tidyr::unite(chr_base, chr,start, sep="_")%>% mutate(sig=neg_log_qvalue > 1.30102 & abs(meth.diff) > 5)->COL_pos


read_tsv("annotated_COL_age_neg_cov20.txt") %>% tidyr::unite(chr_base, chr,start, sep="_")%>% mutate(sig=neg_log_qvalue > 1.30102 & abs(meth.diff) > 5)->COL_neg



read_tsv("annotated_COL_age_pos_cov20.txt") %>% tidyr::unite(chr_base, chr,start, sep="_")%>% mutate(sig=neg_log_qvalue > 1.30102 & abs(meth.diff) > 5)%>% filter(sig==TRUE)
read_tsv("annotated_COL_age_neg_cov20.txt") %>% tidyr::unite(chr_base, chr,start, sep="_")%>% mutate(sig=neg_log_qvalue > 1.30102 & abs(meth.diff) > 5)%>% filter(sig==TRUE)

```








```{r, fig.width=6,fig.height=6}

COL_stem %>% 
  mutate(meth_change = case_when((neg_log_qvalue > 1.30102 & meth.diff > -5) ~ 'hypo',
                                  (neg_log_qvalue > 1.30102 & meth.diff < 5) ~ 'hyper',
                                  TRUE ~ 'no_change'))%>%
add_count(name = 'sample_count') %>%
 group_by(meth_change, sig, sample_count) %>% 
  count() %>% 
ungroup() %>%
 filter(sig != 'FALSE') %>%
 mutate(meth.diff = c(-50,50), 
         neg_log_qvalue = 17, 
       label = paste0(n,  '\n',  
                         round(((n / sample_count) * 100), 1), 
                         '%')) -> COL_stem_val
 


COL_stem%>%
  ggplot(aes(x = meth.diff, y = neg_log_qvalue)) +
 geom_point(aes(color = case_when((neg_log_qvalue > 1.30102 & meth.diff > 5) ~ 'green',
                                  (neg_log_qvalue > 1.30102 & meth.diff < -5) ~ 'red',
                                  TRUE ~ 'gray')),alpha = 3/10) +
     geom_vline(xintercept = c(-5, 5), linetype = 'dashed', color = 'darkgray') +
  geom_hline(yintercept = 1.3, linetype = 'dashed', color = 'darkgray') +
  coord_cartesian(xlim=c(-100,100),ylim = c(0,20))+ 
    geom_text(data = COL_stem_val, aes(label = label), size = 10) +
    scale_color_manual(values = c('gray', 'orangered3', 'aquamarine4')) +
    theme_classic() +
  theme(legend.position = "none")+
  ylab("-Log(qvalue)")+
  xlab("% Methylation change\n (Nonstem-Stem)")+

  ggtitle('Nonstem vs Stem (4mo)')+      
  theme_classic(base_size = 20 ) +
  theme(axis.text.y= element_text(face='bold'),axis.text.x= element_text( face='bold'),title =element_text( face='bold'))+
  theme(legend.position = 'none') ->pC





```








```{r, fig.width=6,fig.height=6}


COL_nonstem %>% 
  mutate(meth_change = case_when((neg_log_qvalue > 1.30102 & meth.diff > -5) ~ 'hypo',
                                  (neg_log_qvalue > 1.30102 & meth.diff < 5) ~ 'hyper',
                                  TRUE ~ 'no_change'))%>%
add_count(name = 'sample_count') %>%
 group_by(meth_change, sig, sample_count) %>% 
  count() %>% 
ungroup() %>%
 filter(sig != 'FALSE') %>%
 mutate(meth.diff = c(-50 ,50), 
         neg_log_qvalue = 17, 
       label = paste0(n,  '\n', 
                         round(((n / sample_count) * 100), 1), 
                         '%')) -> COL_nonstem_val
 



COL_nonstem%>%
  ggplot(aes(x = meth.diff, y = neg_log_qvalue)) +
 geom_point(aes(color = case_when((neg_log_qvalue > 1.30102 & meth.diff > 5) ~ 'green',
                                  (neg_log_qvalue > 1.30102 & meth.diff < -5) ~ 'red',
                                  TRUE ~ 'gray')),alpha = 3/10) +
     geom_vline(xintercept = c(-5, 5), linetype = 'dashed', color = 'darkgray') +
  geom_hline(yintercept = 1.3, linetype = 'dashed', color = 'darkgray') +
  coord_cartesian(xlim=c(-100,100),ylim = c(0,20))+ 
  geom_text(data = COL_nonstem_val, aes(label = label), size = 10) +
    scale_color_manual(values = c('gray', 'orangered3', 'aquamarine4')) +
    theme_classic() +
  theme(legend.position = "none")+
  ylab("-Log(qvalue)")+
  xlab("% Methylation change\n (Nonstem-Stem)")+

  ggtitle('Nonstem vs Stem (24mo)')+  
      theme_classic(base_size = 20 ) +
  theme(axis.text.y= element_text(face='bold'),axis.text.x= element_text( face='bold'),title =element_text( face='bold'))+
  theme(legend.position = 'none')->pD





```






```{r, fig.width=6,fig.height=6}




COL_pos%>% 
  mutate(meth_change = case_when((neg_log_qvalue > 1.30102 & meth.diff > 5) ~ 'hyper',
                                  (neg_log_qvalue > 1.30102 & meth.diff < -5) ~ 'hypo',
                                  TRUE ~ 'no_change'))%>%
add_count(name = 'sample_count') %>%
 group_by(meth_change, sig, sample_count) %>% 
  count() %>% 
ungroup() %>%
 filter(sig != 'FALSE') %>%
 mutate(meth.diff = c(50 ,-50), 
         neg_log_qvalue = 17, 
         label = paste0(n,  '\n', 
                         round(((n / sample_count) * 100),1), 
                         '%')) -> COL_pos_val
 


COL_pos%>%
  ggplot(aes(x = meth.diff, y = neg_log_qvalue)) +
 geom_point(aes(color = case_when((neg_log_qvalue > 1.30102 & meth.diff > 5) ~ 'green',
                                  (neg_log_qvalue > 1.30102 & meth.diff < -5) ~ 'red',
                                  TRUE ~ 'gray')),alpha = 3/10) +
     geom_vline(xintercept = c(-5, 5), linetype = 'dashed', color = 'darkgray') +
  geom_hline(yintercept = 1.3, linetype = 'dashed', color = 'darkgray') +
  coord_cartesian(xlim=c(-100,100),ylim = c(0,20))+
 geom_text(data = COL_pos_val, aes(label = label), size = 10) +
    scale_color_manual(values = c('gray', 'orangered3', 'aquamarine4')) +
    theme_classic() +
  theme(legend.position = "none")+
  ylab("-Log(qvalue)")+
  xlab("% Methylation change\n (Old-young)")+
    ggtitle('24mo vs 4mo (Stem)')+
      theme_classic(base_size = 20 ) +
  theme(axis.text.y= element_text(face='bold'),axis.text.x= element_text( face='bold'),title =element_text( face='bold'))+
  theme(legend.position = 'none') ->pE
```





```{r, fig.width=6,fig.height=6}



COL_neg%>% 
  mutate(meth_change = case_when((neg_log_qvalue > 1.30102 & meth.diff > 5) ~ 'hyper',
                                  (neg_log_qvalue > 1.30102 & meth.diff < -5) ~ 'hypo',
                                  TRUE ~ 'no_change'))%>%
add_count(name = 'sample_count') %>%
 group_by(meth_change, sig, sample_count) %>% 
  count() %>% 
ungroup() %>%
 filter(sig != 'FALSE') %>%
 mutate(meth.diff = c(50 ,-50), 
         neg_log_qvalue = 17, 
       label = paste0(n,  '\n', 
                         round(((n / sample_count) * 100), 1), 
                         '%')) -> COL_neg_val
 


COL_neg%>%
  ggplot(aes(x = meth.diff, y = neg_log_qvalue)) +
 geom_point(aes(color = case_when((neg_log_qvalue > 1.30102 & meth.diff > 5) ~ 'green',
                                  (neg_log_qvalue > 1.30102 & meth.diff < -5) ~ 'red',
                                  TRUE ~ 'gray')),alpha = 3/10) +
     geom_vline(xintercept = c(-5, 5), linetype = 'dashed', color = 'darkgray') +
  geom_hline(yintercept = 1.3, linetype = 'dashed', color = 'darkgray') +
  coord_cartesian(xlim=c(-100,100),ylim = c(0,20))+
 geom_text(data = COL_neg_val, aes(label = label), size = 10) +
    scale_color_manual(values = c('gray', 'orangered3', 'aquamarine4')) +
    theme_classic() +
  theme(legend.position = "none")+
  ylab("-Log(qvalue)")+
  xlab("% Methylation change\n (Old-young)")+
    ggtitle('24mo vs 4mo (Nonstem)')+
      theme_classic(base_size = 20) +
  theme(axis.text.y= element_text(face='bold'),axis.text.x= element_text( face='bold'),title =element_text( face='bold'))+
  theme(legend.position = 'none') ->pF

```






```{r}
vroom("annotated_COL_age_pos_cov20.txt") %>%
  select(chr:location) -> COL_pos_perm
vroom("annotated_COL_age_neg_cov20.txt") %>%
  select(chr:location) -> COL_neg_perm

rbind(COL_pos_perm, COL_neg_perm) %>%
  unite(temp, c(meth.diff, qvalue), sep = '_') %>%
  select(chr, start, location, temp) %>%
  pivot_wider(names_from = location, values_from = temp) %>%
  na.omit() %>%
  separate(COL_pos, into = c('COL_pos_meth.diff', 'COL_pos_qvalue'), 
           sep = '_', convert = T) %>%
  separate(COL_neg, into = c('COL_neg_meth.diff', 'COL_neg_qvalue'), 
           sep = '_', convert = T) %>%
  mutate(sig_COL_pos = ifelse((abs(COL_pos_meth.diff) > 5 & COL_pos_qvalue < 0.05), 'sig', 'nonsig'),
         sig_COL_neg = ifelse((abs(COL_neg_meth.diff) > 5 & COL_neg_qvalue < 0.05), 'sig', 'nonsig')) -> COL_overlaps
```

Do scatterplot filter for statistically significant as well and you will see same numbers

#### Filtered for Significant in One Condition, but then looking at concordance/discordance

```{r, fig.width=6,fig.height=6}
### quadrant counts
COL_overlaps %>%
  filter(sig_COL_pos == 'sig' | sig_COL_neg == 'sig') %>%
  mutate(quadrant = case_when(COL_pos_meth.diff >= 0 & COL_neg_meth.diff >= 0 ~ 'both_hyper',
                              COL_pos_meth.diff < 0 & COL_neg_meth.diff >= 0 ~ 'pos_hypo_neg_hyper',
                              COL_pos_meth.diff >= 0 & COL_neg_meth.diff < 0 ~ 'pos_hyper_neg_hypo',
                              COL_pos_meth.diff < 0 & COL_neg_meth.diff < 0 ~ 'both_hypo')) %>%
  count(quadrant) %>%
  mutate(COL_pos_meth.diff = c(80, -80, 80, -80),
         COL_neg_meth.diff = c(80, -80, -80, 80)) -> COL_quad_counts








COL_overlaps %>% filter(sig_COL_pos == 'sig' | sig_COL_neg == 'sig')->COL_pos_neg_3

cor.test(COL_pos_neg_3$COL_pos_meth.diff, COL_pos_neg_3$COL_neg_meth.diff)%>% broom::tidy()->COL_pos_neg_4

COL_pos_neg_4%>%
    mutate(COL_pos_meth.diff = 40, COL_neg_meth.diff = -60,
                      p_val=case_when(p.value<=0.001 ~ "<0.001",
                         between(p.value,0.001, 0.01)~"<0.01",
                         between(p.value,0.01, 0.05)~"<0.05",
                         between(p.value,0.05, 0.1)~"<0.1",
                           TRUE~ ">= 0.1"),
         label = paste0('r = ', round(estimate, 2), '\n', 
                        'p = ', p_val, '\n')) -> COL_pos_neg_5




COL_overlaps %>%
  filter(sig_COL_pos == 'sig' | sig_COL_neg == 'sig') %>%
ggplot(aes(x = COL_pos_meth.diff, COL_neg_meth.diff)) +
    geom_point(color="navy") +
  geom_vline(xintercept = c(0), linetype = 'dashed', color = 'gray60') +
  geom_hline(yintercept = c(0), linetype = 'dashed', color = 'gray60') +
  coord_cartesian(xlim = c(-100, 100), ylim = c(-100, 100)) +
  geom_smooth(method = lm, se = F, linetype="dashed", size=2, color="RED")+
  # geom_text(data = COL_quad_counts, aes(label = n),size=7) +
     geom_text(data = COL_pos_neg_5, aes(label = label), size = 10) +
  labs(title = 'Stem vs Nonstem (COL)', x = '% Change in Stem Cells',
       y = '% Change in Non-stem Cells') +
   theme_classic(base_size = 22) +
  theme(axis.text.y= element_text(face='bold'),axis.text.x= element_text( face='bold'),title =element_text( face='bold'))+
  theme(legend.position = 'none', 
             strip.text = element_text(size = 22))->pG


 write_tsv(COL_overlaps, "COL_overlaps.tsv")
```





```{r}
vroom("annotated_LSI_age_pos_cov20.txt") %>%
  select(chr:location) -> LSI_pos_perm
vroom("annotated_LSI_age_neg_cov20.txt") %>%
  select(chr:location) -> LSI_neg_perm

rbind(LSI_pos_perm, LSI_neg_perm) %>%
  unite(temp, c(meth.diff, qvalue), sep = '_') %>%
  select(chr, start, location, temp) %>%
  pivot_wider(names_from = location, values_from = temp) %>%
  na.omit() %>%
  separate(LSI_pos, into = c('LSI_pos_meth.diff', 'LSI_pos_qvalue'), 
           sep = '_', convert = T) %>%
  separate(LSI_neg, into = c('LSI_neg_meth.diff', 'LSI_neg_qvalue'), 
           sep = '_', convert = T) %>%
  mutate(sig_LSI_pos = ifelse((abs(LSI_pos_meth.diff) > 5 & LSI_pos_qvalue < 0.05), 'sig', 'nonsig'),
         sig_LSI_neg = ifelse((abs(LSI_neg_meth.diff) > 5 & LSI_neg_qvalue < 0.05), 'sig', 'nonsig')) -> LSI_overlaps
```

Do scatterplot filter for statistically significant as well and you will see same numbers

#### Filtered for Significant in One Condition, but then looking at concordance/discordance

```{r, fig.width=6,fig.height=6}
### quadrant counts
LSI_overlaps %>%
  filter(sig_LSI_pos == 'sig' | sig_LSI_neg == 'sig') %>%
  mutate(quadrant = case_when(LSI_pos_meth.diff >= 0 & LSI_neg_meth.diff >= 0 ~ 'both_hyper',
                              LSI_pos_meth.diff < 0 & LSI_neg_meth.diff >= 0 ~ 'pos_hypo_neg_hyper',
                              LSI_pos_meth.diff >= 0 & LSI_neg_meth.diff < 0 ~ 'pos_hyper_neg_hypo',
                              LSI_pos_meth.diff < 0 & LSI_neg_meth.diff < 0 ~ 'both_hypo')) %>%
  count(quadrant) %>%
  mutate(LSI_pos_meth.diff = c(80, -80, 80, -80),
         LSI_neg_meth.diff = c(80, -80, -80, 80)) -> LSI_quad_counts








LSI_overlaps %>% filter(sig_LSI_pos == 'sig' | sig_LSI_neg == 'sig')->LSI_pos_neg_3

cor.test(LSI_pos_neg_3$LSI_pos_meth.diff, LSI_pos_neg_3$LSI_neg_meth.diff)%>% broom::tidy()->LSI_pos_neg_4

LSI_pos_neg_4%>%
    mutate(LSI_pos_meth.diff = 40, LSI_neg_meth.diff = -60,
                      p_val=case_when(p.value<=0.001 ~ "<0.001",
                         between(p.value,0.001, 0.01)~"<0.01",
                         between(p.value,0.01, 0.05)~"<0.05",
                         between(p.value,0.05, 0.1)~"<0.1",
                           TRUE~ ">= 0.1"),
         label = paste0('r = ', round(estimate, 2), '\n', 
                        'p = ', p_val, '\n')) -> LSI_pos_neg_5




LSI_overlaps %>%
  filter(sig_LSI_pos == 'sig' | sig_LSI_neg == 'sig') %>%
ggplot(aes(x = LSI_pos_meth.diff, LSI_neg_meth.diff)) +
    geom_point(color="navy") +
  geom_vline(xintercept = c(0), linetype = 'dashed', color = 'gray60') +
  geom_hline(yintercept = c(0), linetype = 'dashed', color = 'gray60') +
  coord_cartesian(xlim = c(-100, 100), ylim = c(-100, 100)) +
  geom_smooth(method = lm, se = F, linetype="dashed", size=2, color="red")+
  # geom_text(data = LSI_quad_counts, aes(label = n),size=7) +
     geom_text(data = LSI_pos_neg_5, aes(label = label), size = 10) +
  labs(title = 'Stem vs Nonstem (LSI)', x = '% Change in Stem Cells',
       y = '% Change in Non-stem Cells') +
 theme_classic(base_size = 22) +
  theme(axis.text.y= element_text(face='bold'),axis.text.x= element_text( face='bold'),title =element_text( face='bold'))+
  theme(legend.position = 'none', 
             strip.text = element_text(size = 22))->pH

```









```{r}
vroom("annotated_USI_age_pos_cov20.txt") %>%
  select(chr:location) -> USI_pos_perm
vroom("annotated_USI_age_neg_cov20.txt") %>%
  select(chr:location) -> USI_neg_perm

rbind(USI_pos_perm, USI_neg_perm) %>%
  unite(temp, c(meth.diff, qvalue), sep = '_') %>%
  select(chr, start, location, temp) %>%
  pivot_wider(names_from = location, values_from = temp) %>%
  na.omit() %>%
  separate(USI_pos, into = c('USI_pos_meth.diff', 'USI_pos_qvalue'), 
           sep = '_', convert = T) %>%
  separate(USI_neg, into = c('USI_neg_meth.diff', 'USI_neg_qvalue'), 
           sep = '_', convert = T) %>%
  mutate(sig_USI_pos = ifelse((abs(USI_pos_meth.diff) > 5 & USI_pos_qvalue < 0.05), 'sig', 'nonsig'),
         sig_USI_neg = ifelse((abs(USI_neg_meth.diff) > 5 & USI_neg_qvalue < 0.05), 'sig', 'nonsig')) -> USI_overlaps
```

Do scatterplot filter for statistically significant as well and you will see same numbers

#### Filtered for Significant in One Condition, but then looking at concordance/discordance

```{r, fig.width=6,fig.height=6}
### quadrant counts
USI_overlaps %>%
  filter(sig_USI_pos == 'sig' | sig_USI_neg == 'sig') %>%
  mutate(quadrant = case_when(USI_pos_meth.diff >= 0 & USI_neg_meth.diff >= 0 ~ 'both_hyper',
                              USI_pos_meth.diff < 0 & USI_neg_meth.diff >= 0 ~ 'pos_hypo_neg_hyper',
                              USI_pos_meth.diff >= 0 & USI_neg_meth.diff < 0 ~ 'pos_hyper_neg_hypo',
                              USI_pos_meth.diff < 0 & USI_neg_meth.diff < 0 ~ 'both_hypo')) %>%
  count(quadrant) %>%
  mutate(USI_pos_meth.diff = c(85, -85, 85, -85),
         USI_neg_meth.diff = c(85, -85, -85, 85)) -> USI_quad_counts








USI_overlaps %>% filter(sig_USI_pos == 'sig' | sig_USI_neg == 'sig')->USI_pos_neg_3

cor.test(USI_pos_neg_3$USI_pos_meth.diff, USI_pos_neg_3$USI_neg_meth.diff)%>% broom::tidy()->USI_pos_neg_4

USI_pos_neg_4%>%
    mutate(USI_pos_meth.diff = 40, USI_neg_meth.diff = -60,
                      p_val=case_when(p.value<=0.001 ~ "<0.001",
                         between(p.value,0.001, 0.01)~"<0.01",
                         between(p.value,0.01, 0.05)~"<0.05",
                         between(p.value,0.05, 0.1)~"<0.1",
                           TRUE~ ">= 0.1"),
         label = paste0('r = ', round(estimate, 2), '\n', 
                        'p = ', p_val, '\n')) -> USI_pos_neg_5




USI_overlaps %>%
  filter(sig_USI_pos == 'sig' | sig_USI_neg == 'sig') %>%
ggplot(aes(x = USI_pos_meth.diff, USI_neg_meth.diff)) +
    geom_point(color="navy") +
  geom_vline(xintercept = c(0), linetype = 'dashed', color = 'gray60') +
  geom_hline(yintercept = c(0), linetype = 'dashed', color = 'gray60') +
  coord_cartesian(xlim = c(-100, 100), ylim = c(-100, 100)) +
  geom_smooth(method = lm, se = F, linetype="dashed", size=2, color="RED")+
  # geom_text(data = USI_quad_counts, aes(label = n),size=8) +
     geom_text(data = USI_pos_neg_5, aes(label = label), size = 10) +
  labs(title = 'Stem vs Nonstem (USI)', x = '% Change in Stem Cells',
       y = '% Change in Non-stem Cells') +
 theme_classic(base_size = 22) +
  theme(axis.text.y= element_text(face='bold'),axis.text.x= element_text( face='bold'),title =element_text( face='bold'))+
  theme(legend.position = 'none', 
             strip.text = element_text(size = 22))->pI

```





```{r, fig.width=6,fig.height=4}
df <- data.frame()
  ggplot(df) + geom_blank() + xlim(0, 10) + ylim(0, 100)+theme_void()->p8

```



```{r, fig.width=22,fig.height=20}



(((p8+pB) +plot_layout(width = c(1.5,1)))/((pC|pD|pE|pF)+plot_layout(width = c(1)))/((p8|pG|pH|pI|p8)+plot_layout(width = c(0.2,0.5,0.5,0.5,0.2)))+ plot_layout(nrow =3,heights = c(0.5,0.3, 0.3)))
 



                                          
```


























